---
title: "Assignment 5"
author: "Becky Clow, Eamon Devlin, and Madeline Gorchels"
date: "11/26/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r} 
#Reading in the packages 
library(tidyverse)
library(kableExtra)
library(effsize)
library(stargazer)
#Reading in the data frames
grad_enrollment = read_csv("Grad enrollment 1967 - 2015.csv")
doctoral_salary = read_csv("Median salary for doctoral recipients.csv")
#This csv need further editing 
phd_field_gender = read_csv("PhDs by Field 1985 - 2015.csv")
faculty_salary = read_csv("Faculty salary data (2008 - 2009 survey).csv")

#For your viewing pleasure 
#View(grad_enrollment)
#View(doctoral_salary)
#View(phd_field_gender)
#View(faculty_salary)
```
3) Male and female salaries for starting postdoctoral and other employment positions (2015). Compare median salaries for male and female doctorate recipients in 2015. Answer these two questions:Does median salary differ significantly between male and female starting postdoc positions? Does median salary differ significantly between male and female PhD recipients in non-postdoc employment positions?


```{r}

```

4) Exploring academic salaries for professors in U.S. colleges. Explore relationships between variables in the ‘Faculty salary data (2008 - 2009 survey)’ dataset. Develop a model describing faculty salary based on data for faculty sex, rank, years in current position, field, and number of years since doctoral degree was earned. You should make decisions regarding which variables should remain in your final model. Describe the results qualitatively and quantitatively (i.e., don’t just report the statistical
results of the model – make sure you describe interesting findings in text). You can also discuss any concerns that you have with the model(s) you present, if any.

```{r}
#Starting the linear model 
salary_mod_1 = lm(salary~sex+years_faculty_service+faculty_rank+discipline, data = faculty_salary)
summary(salary_mod_1)

salary_mod
```

```{r}

```

