---
title: "Assignment 5"
author: "Becky Clow, Eamon Devlin, and Madeline Gorchels"
date: "11/26/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r} 
#Reading in the packages 
library(tidyverse)
library(kableExtra)
library(effsize)
library(stargazer)
library(car)
library(reshape2)

#Reading in the data frames
grad_enrollment = read_csv("Grad enrollment 1967 - 2015.csv")
doctoral_salary = read_csv("Median salary for doctoral recipients.csv")
#This csv need further editing 
phd_field_gender = read_csv("PhDs by Field 1985 - 2015.csv")
faculty_salary = read_csv("Faculty salary data (2008 - 2009 survey).csv")

#formatted  phd_field_gender
rev_phd_field = read_csv("PhDs_rev.csv")

phd_transpose = read_csv("phd_transpose.csv")

#For your viewing pleasure 
#View(grad_enrollment)
#View(doctoral_salary)
#View(phd_field_gender)
#View(faculty_salary)
```

1) Male and female graduate enrollment (1967 - 2015). Compare trends in total graduate enrollment
for males and females (including full-time/part-time and private/public universities) in the United
States from 1967 - 2015. Describe your results statistically, graphically and in text.

```{r}
#Exploritory scatter graphs

#scatter for women
grad_w_scatter <- ggplot(grad_enrollment, aes(x = year, y = total_women)) +
  geom_point()
grad_w_scatter
#Looks good and linear

#scatter for men
grad_m_scatter <- ggplot(grad_enrollment, aes(x = year, y = total_men)) +
  geom_point()
grad_m_scatter
#Not linear, What do we do??
```

```{r}
#Regression to look at total of males vs females in grad school from 1967-2015

#linear model for women
women_model <- lm(total_women ~ year, data = grad_enrollment)
women_model
summary(women_model)
women_r <- cor.test(grad_enrollment$total_women, grad_enrollment$year)
women_r

#linear model for men
men_model <- lm(total_men ~ year, data = grad_enrollment)
men_model
summary(men_model)
men_r <- cor.test(grad_enrollment$total_men, grad_enrollment$year)
men_r

```

```{r}
#Model diagnostics
plot(women_model)

plot(men_model)

#everythig looks weird here not sure this is right!
```


```{r}
#line graph
grad_enrol_graph <- ggplot(grad_enrollment, aes(year)) +
  geom_point(aes(y = total_women, color = "Women")) +
  geom_point(aes(y = total_men, color = "Men")) +
  theme_classic() +
  geom_smooth(method = lm, se = TRUE, size = 0.5, (aes(y = total_women)), color = "turquoise") +
  geom_smooth(method = lm, se = TRUE, size = 0.5, (aes(y = total_men)), color = "coral2") +
  scale_x_continuous() +
  labs(x = "Year", y = "Number of Graduate Students Enrolled")+ #need to fix ledgend and colors 
  scale_color_discrete(name = "Gender", labels = c("Men", "Women"))

grad_enrol_graph

```
##2) Shifts in female PhD recipients by field (1985, 2000, and 2015). 
Describe if and how there was a shift in PhDs awarded to females in four fields (Physical and Earth Sciences, Engineering, Education,
and Humanities & Arts) in 1985, 2000, and 2015. Describe your results statistically, in a graph or table, and in text. Note: There are several ways that you can interpret this question. You are invited to decide
which you think is/are most interesting. Just be really clear about what you are asking/answering in
your report.

```{r}

# First want to create a female subset with only years 1985, 2000, and 2015
rev_phd_field$Field_of_study_and_sex <- factor(rev_phd_field$Field_of_study_and_sex)

female_field <- filter(rev_phd_field, Field_of_study_and_sex %in% c("Female_life_sci","Female_phy_sci","Female_math","Female_ss", "Female_eng","Female_ed","Female_art","Female_other"))

# Note, I also removed "Female_all"

# Now to remove the %'s

female_absolute_field <- select(female_field, "1985_Number", "2000_Number", "2015_Number") 

rownames(female_absolute_field) <- c("Female_life_sci","Female_phy_sci","Female_math","Female_ss", "Female_eng","Female_ed","Female_art","Female_other")


f_phd_prop_all <- prop.table(as.matrix(female_absolute_field), 2)

f_phd_chi_all <- chisq.test(female_absolute_field)

f_phd_chi_all

# p-value = < 2.2 e -16 so DEFINETLY a significant difference
```

```{r}
# Making a nice table

trim_number_all <- subset(female_absolute_field, rownames(f_phd_prop_all) %in% c("Female_phy_sci","Female_eng", "Female_ed","Female_art"))

pre_kable <- mutate(trim_number_all, Field = c("Physical & Earth Sciences","Engineering","Education","Arts & Humanities"))

pre_kable_select <- select(pre_kable, "Field", "1985_Number","2000_Number","2015_Number")


#rownames(trim_number_all) <- c("Female_phy_sci","Female_eng","Female_ed","Female_art")

trim_prop_all <- subset(f_phd_prop_all, rownames(f_phd_prop_all) %in% c("Female_phy_sci","Female_eng", "Female_ed","Female_art"))
  
chi_table_4 <- kable(pre_kable_select, col.names = c("Field","1985", "2000", "2015"), 
                       caption = "Changes in Fields of Study") %>% 
  kable_styling(c("striped","border"))  # %>% 
 

chi_table_4



lob_prop_final = as.data.frame(legal_lob) %>%
  rbind(., c(386, 1282)) %>% 
  mutate(Site = c("Arroyo Quemado", "Carpineria", "Isla Vista", "Mohawk", "Naples", "Total"),
         AboveLimit_percentage = round(AboveLimit/(AboveLimit+BelowLimit), 2),
         BelowLimit_percentage = round(BelowLimit/(AboveLimit+BelowLimit), 2),
         Legal = paste(as.character(AboveLimit),"(",as.character(AboveLimit_percentage),")"),
         Not_legal = paste(as.character(BelowLimit),"(",as.character(BelowLimit_percentage),")"),
         Total = AboveLimit+BelowLimit) %>% 
  select(Site, Legal, Not_legal, Total) %>% 
  kable(col.name = c("Site", "Above Limit", "Below Limit", "Total")) %>% 
  kable_styling()

lob_prop_final
```



```{r}

# This run will look at just the 4 specified fields

female_field_4 <- filter(rev_phd_field, Field_of_study_and_sex %in% c("Female_phy_sci","Female_eng","Female_ed","Female_art"))

# Note, I also removed "Female_all"

# Now to remove the %'s

female_absolute_field_4 <- select(female_field_4, "1985_Number", "2000_Number", "2015_Number") 

f_4 <- as.data.frame(f_phd_prop_all_4) %>% 
  mutate(., Field = c("Physical & Earth Sciences","Engineering","Education","Arts & Humanities"))

f_5 <- f_4
#colnames(f_5, c("1985_prop", "2000_prop", "2015_prop", "Field"))
colnames(f_5)[1] <- "1985"
colnames(f_5)[2] <- "2000"
colnames(f_5)[3] <- "2015"

f_6 <- merge(pre_kable_select,f_5,by="Field") 
f_7 <- round(f_6$`1985_prop`,2)

f_4_long <- melt(f_4, id.vars=c("Field"), value.name = "proportion")
names (f_4_long) [2] <-paste("Year")

f_5_long <- melt(f_5, id.vars=c("Field"), value.name = "Proportion")
names (f_5_long) [2] <-paste("Year")

rownames(female_absolute_field_4) <- c("Female_phy_sci", "Female_eng","Female_ed","Female_art")


f_phd_prop_all_4 <- prop.table(as.matrix(female_absolute_field_4), 2)

f_phd_chi_all_4 <- chisq.test(female_absolute_field_4)

f_phd_chi_all_4

# p-value = < 2.2 e -16 so DEFINETLY a significant difference

```


```{r}

# I think this crunk is meaningless now...

#phd_transpose$Field_of_study_and_sex <- factor(rev_phd_field$Field_of_study_and_sex)

#female_field_t <- select(phd_transpose, Field_of_study_and_sex, #%in%
                         #"Female_life_sci","Female_phy_sci","Female_math","Female_ss", #"Female_eng","Female_ed","Female_art","Female_other")

# Note, I also removed "Female_all"

# Now to remove the %'s

#female_absolute_field_t <- filter(female_field_t,Field_of_study_and_sex %in% c("1985_Number", "2000_Number", "2015_Number")) 

#rownames(female_absolute_field_t) <- c("1985_Number","2000_Number", "2015_Number")

#phd_f_row <- select(female_absolute_field_t, "Female_life_sci":"Female_other")

#f_phd_t_prop_all <- prop.table(as.matrix(phd_f_row), 3)

#f_phd_t_chi_all <- chisq.test(female_absolute_field_t)

#f_phd_chi_all
```

Ploting data

```{r}
ggplot(data = TTM, aes(x = Type.of.Behavior, y = Sample.Size, fill = Stage.of.Change)) + 
    geom_bar()

stack_bar <- ggplot(data = f_4, aes(x = c("1985_Number", "2000_Number", "2015_Number"), y = c("1985_Number", "2000_Number", "2015_Number"), fill = Field)) + 
    geom_bar()

stack_bar


bar_stack <- table(f_4$`1985_Number`, f_4$`2015_Number`)
barplot(counts, main="Car Distribution by Gears and VS",
  xlab="Number of Gears", col=c("darkblue","red"),
 	legend = rownames(counts))


bar <- barplot(f_phd_prop_all_4, xlab = "Year",col = 1:4)


stacking_bars <- ggplot() +
  geom_bar(aes(y = Proportion,
               x = Year,
               fill = Field),
           data = f_5_long,
           stat="identity") +
  theme_classic() +
  scale_y_continuous(expand = c(0,0)) +
  scale_fill_manual(values = c("chartreuse3","blue3","cyan3","brown2"), name = "Field of Study" ) 
 
 
stacking_bars


```


3) Male and female salaries for starting postdoctoral and other employment positions (2015). Compare median salaries for male and female doctorate recipients in 2015. Answer these two questions:Does median salary differ significantly between male and female starting postdoc positions? Does median salary differ significantly between male and female PhD recipients in non-postdoc employment positions?

```{r}
post_doc_hist = ggplot(doctoral_salary, aes(x = men_postdoc))+
  geom_histogram()
post_doc_hist
post_doc_qq = ggplot(doctoral_salary, aes(x = men_postdoc))+
  geom_qq()
#post_doc_qq
```


```{r}

#var.test(doctoral_salary$men_employment,doctoral_salary$women_employment) #Variances are not equal 
#var.test(doctoral_salary$men_postdoc,doctoral_salary$women_postdoc) #Variances are not equal 

non_post_doc_test = wilcox.test(doctoral_salary$men_employment,doctoral_salary$women_employment, paired = TRUE)

post_doc_test = wilcox.test(doctoral_salary$men_postdoc,doctoral_salary$women_postdoc, paired = TRUE)

post_doc_test
non_post_doc_test
```


```{r}
#boxplot of salaries

#data is tidy format
salary_tidy <- doctoral_salary %>% 
  gather(emplo_type, salary, `men_employment`:`women_postdoc`)

#boxplot code
salary_box <- ggplot(salary_tidy, aes(x = emplo_type, y = salary)) +
  geom_boxplot()
#salary_box

#boxplot employment
salary_employ <- salary_tidy %>% 
  filter(emplo_type == "men_employment"|
         emplo_type == "women_employment")

salary_employ_box <- ggplot(salary_employ, aes(x = emplo_type, y = salary)) +
  geom_boxplot() +
  theme_classic() +
  scale_x_discrete(labels = c("Men", "Women")) +
  ylab("Annual Salary (dollars)") +
  xlab("Non-academic Employment")
salary_employ_box


```

```{r}
#boxplot postdoc
salary_postdoc <- salary_tidy %>% 
  filter(emplo_type == "men_postdoc"|
         emplo_type == "women_postdoc")

salary_postdoc_box <- ggplot(salary_postdoc, aes(x = emplo_type, y = salary)) +
  geom_boxplot(fill = "cyan3") +
  theme_classic() +
  scale_x_discrete(labels = c("Men", "Women")) +
  ylab("Annual Salary (dollars)") +
  xlab("Postdoc Employment")
salary_postdoc_box
```


Part 4
```{r}
#Starting the linear model 
salary_mod_1 = lm(salary~sex+years_faculty_service+years_since_PhD+faculty_rank+discipline, data = faculty_salary)
summary(salary_mod_1)

salary_mod_1
```

```{r}
#Assistant professors < Acossiate professors < Full professor
plot(salary_mod_1)
#hmmm it seems there is some heterdasicity, it also has some issues with residual normality 
vif(salary_mod_1)
AIC(salary_mod_1)

```

```{r}
#Making a model that excludes years
salary_mod_2 = lm(salary~sex+faculty_rank+discipline, data = faculty_salary)
summary(salary_mod_2)
AIC(salary_mod_2)
plot(salary_mod_2)
vif(salary_mod_2)

```

```{r}
salary_mod_3 = lm(salary~sex+faculty_rank+years_faculty_service+discipline, data = faculty_salary)
summary(salary_mod_3)
AIC(salary_mod_3)
vif(salary_mod_3)
```
```{r}
faculty_sal_acoc = faculty_salary %>% 
  filter(faculty_rank == "AssocProf")
faculty_sal_asst = faculty_salary %>% 
  filter(faculty_rank == "AsstProf")
faculty_sal_prof = faculty_salary %>% 
  filter(faculty_rank == "Prof")

```
```{r, results='asis'}
constillations = stargazer(salary_mod_2, type = "html")
constillations 
```



```{r}
salary_mod_4 = lm(salary~sex+years_since_PhD+faculty_rank+discipline, data = faculty_salary)
vif(salary_mod_4)
summary(salary_mod_4)
AIC(salary_mod_4)
```

```{r}
salary_mod_5 = lm(salary~sex+years_faculty_service+faculty_rank+discipline+years_faculty_service*faculty_rank, data = faculty_salary)
summary(salary_mod_5)

```

