---
title: "Assignment 5"
author: "Becky Clow, Eamon Devlin, and Madeline Gorchels"
date: "11/26/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r} 
#Reading in the packages 
library(tidyverse)
library(kableExtra)
library(effsize)
library(stargazer)
library(car)

#Reading in the data frames
grad_enrollment = read_csv("Grad enrollment 1967 - 2015.csv")
doctoral_salary = read_csv("Median salary for doctoral recipients.csv")
#This csv need further editing 
phd_field_gender = read_csv("PhDs by Field 1985 - 2015.csv")
faculty_salary = read_csv("Faculty salary data (2008 - 2009 survey).csv")

#For your viewing pleasure 
#View(grad_enrollment)
#View(doctoral_salary)
#View(phd_field_gender)
#View(faculty_salary)
```

1) Male and female graduate enrollment (1967 - 2015). Compare trends in total graduate enrollment
for males and females (including full-time/part-time and private/public universities) in the United
States from 1967 - 2015. Describe your results statistically, graphically and in text.

```{r}
#Exploritory scatter graphs

#scatter for women
grad_w_scatter <- ggplot(grad_enrollment, aes(x = year, y = total_women)) +
  geom_point()
grad_w_scatter
#Looks good and linear

#scatter for men
grad_m_scatter <- ggplot(grad_enrollment, aes(x = year, y = total_men)) +
  geom_point()
grad_m_scatter
#Not linear, What do we do??
```

```{r}
#Regression to look at total of males vs females in grad school from 1967-2015

#linear model for women
women_model <- lm(total_women ~ year, data = grad_enrollment)
women_model
summary(women_model)

#linear model for men
men_model <- lm(total_men ~ year, data = grad_enrollment)
men_model
summary(men_model)

```

```{r}
#Model diagnostics
plot(women_model)

plot(men_model)

#everythig looks weird here not sure this is right!
```


```{r}
#line graph
grad_enrol_graph <- ggplot(grad_enrollment, aes(year)) +
  geom_point(aes(y = total_women, color = "Women")) +
  geom_point(aes(y = total_men, color = "Men")) +
  theme_classic() +
  geom_smooth(method = lm, se = TRUE, size = 0.5, (aes(y = total_women)), color = "turquoise") +
  geom_smooth(method = lm, se = TRUE, size = 0.5, (aes(y = total_men)), color = "orange") +
  scale_x_continuous() +
  labs(x = "Year", y = "Number of Graduate Students Enrolled") #need to fix ledgend and colors

grad_enrol_graph


```


3) Male and female salaries for starting postdoctoral and other employment positions (2015). Compare median salaries for male and female doctorate recipients in 2015. Answer these two questions:Does median salary differ significantly between male and female starting postdoc positions? Does median salary differ significantly between male and female PhD recipients in non-postdoc employment positions?


```{r}

```

4) Exploring academic salaries for professors in U.S. colleges. Explore relationships between variables in the ‘Faculty salary data (2008 - 2009 survey)’ dataset. Develop a model describing faculty salary based on data for faculty sex, rank, years in current position, field, and number of years since doctoral degree was earned. You should make decisions regarding which variables should remain in your final model. Describe the results qualitatively and quantitatively (i.e., don’t just report the statistical
results of the model – make sure you describe interesting findings in text). You can also discuss any concerns that you have with the model(s) you present, if any.

```{r}
#Starting the linear model 
salary_mod_1 = lm(salary~sex+years_faculty_service+faculty_rank+discipline, data = faculty_salary)
summary(salary_mod_1)

salary_mod
```

```{r}
#Assistant professors < Acossiate professors < Full professor
plot(salary_mod_1)
#hmmm it seems there is some heterdasicity, it also has some issues with residual normality 
vif(salary_mod_1)
```

```{r}
#Making a model that excludes years
salary_mod_2 = lm(salary~sex+faculty_rank+discipline, data = faculty_salary)
summary(salary_mod_2)
```

```{r}
salary_mod_3 = lm(salary~sex+years_faculty_service+discipline, data = faculty_salary)
summary(salary_mod_3)
```
```{r}
faculty_sal_acoc = faculty_salary %>% 
  filter(faculty_rank == "AssocProf")
faculty_sal_asst = faculty_salary %>% 
  filter(faculty_rank == "AsstProf")
faculty_sal_prof = faculty_salary %>% 
  filter(faculty_rank == "Prof")

interaction_graph = ggplot(faculty_salary, aes(x = years_faculty_service, y = salary)+
  geom_point(data = faculty_sal_acoc, aes(x = years_faculty_service, y = salary))+
  geom_point(data = faculty_sal_asst, aes(x = years_faculty_service, y = salary))

interaction_graph
```

